Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-15 cover_letter.tex
Moved paragraph on perlocutionnary acts to a footnote

\subsection{Rework of the introduction} The paper starts off with a discussion
of Austins speech act theory, including locutionary act, illocutionary force
and perlocutionary act. As the concept of speech acts is not really picked up
in the remainder of the paper, I do not see the point in starting with such a
discussion. It would be more appropriate to motivate how a robot could benefit
from a symbolic knowledge base etc.

>>>>

\subsection{Rework of the introduction}

Reviewer comment: ``The paper starts off with a discussion
of Austins speech act theory, including locutionary act, illocutionary force
and perlocutionary act. As the concept of speech acts is not really picked up
in the remainder of the paper, I do not see the point in starting with such a
discussion. It would be more appropriate to motivate how a robot could benefit
from a symbolic knowledge base etc.''

Austin's \emph{speech acts} were actually one of the starting point of our
analysis of dialogue understanding, and we think it is worthwhile to briefly mention
them in the introduction, as one of the theoritical ground of our work.

The reviewer however rightfully notes that \emph{perlocutionnary acts}, while mentioned, are not
actually used further. We moved this paragraph to a simple footnote.

### 2011-07-15 paper_knowledge.tex
Moved paragraph on perlocutionnary acts to a footnote

\begin{figure}%[!ht] 
	\centering
	\includegraphics[width=0.9\linewidth]{images/pt.jpg} 
	\caption{Interacting with
	the robot in an everyday setup: the human asks for help in vague terms, the
	robot takes into account the human's spatial perspective to refine its
	understanding of the question.} 
	\label{fig|vpt} 
\end{figure}

Second, the \emph{illocutionary force}, \ie the \emph{intent} of the utterance
as thought by the agent, must be extracted and understood. In our example,
Thomas obviously wants an action to be performed by the robot. The action
parametrization is conveyed by the semantics attached to the words and the
grammatical structures of the sentence. In our example, the type of action is
given by the verb ``\textit{give}''. Assuming the robot has some procedural
knowledge attached to this symbol, the action type can be considered as
grounded for the robot. We can as well understand that the recipient of the
action is the human, the performer is the robot itself, and the object acted
upon is the tape. These are the basic \emph{thematic roles}~\cite{Gruber1965}
that can be extracted from the sentence that allow to fully ground the action.

Finally, the implicit speaker's expectation can sometimes be conveyed --the
\emph{perlocutionary act}-- and should be taken into account. If Thomas would
have said instead ``Jido, this box is too heavy for me'', he may implicitly
expect the robot to memorize the fact that the box's weight is over his
capabilities, and it may as well imply that Thomas is requiring help to carry
the box.

>>>>

\begin{figure}%[!ht] 
	\centering
	\includegraphics[width=1.0\linewidth]{images/pt.jpg} 
	\caption{Interacting with
	the robot in an everyday setup: the human asks for help in vague terms, the
	robot takes into account the human's spatial perspective to refine its
	understanding of the question.} 
	\label{fig|vpt} 
\end{figure}

Second, the \emph{illocutionary force}, \ie the \emph{intent} of the utterance
as thought by the agent, must be extracted and understood. In our example,
Thomas obviously wants an action to be performed by the robot. The action
parametrization is conveyed by the semantics attached to the words and the
grammatical structures of the sentence. In our example, the type of action is
given by the verb ``\textit{give}''. Assuming the robot has some procedural
knowledge attached to this symbol, the action type can be considered as
grounded for the robot. We can as well understand that the recipient of the
action is the human, the performer is the robot itself, and the object acted
upon is the tape. These are the basic \emph{thematic roles}~\cite{Gruber1965}
that can be extracted from the sentence that allow to fully ground the action
\footnote{The third class of speech acts, the \emph{perlocutionary acts}, deals
with implicit speaker's expectations. We will not consider it further in this
article}.

%Finally, the implicit speaker's expectation can sometimes be conveyed --the
%\emph{perlocutionary act}-- and should be taken into account. If Thomas would
%have said instead ``Jido, this box is too heavy for me'', he may implicitly
%expect the robot to memorize the fact that the box's weight is over his
%capabilities, and it may as well imply that Thomas is requiring help to carry
%the box.
